### 2022-10-13 dissertation/chapters/01-introduction.tex
✨ (disseration): Chapter 2 - Done

\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}. A popular field of focus for studying \acp{ANN} is the process by which these models are trained.  The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised. The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acl{HH} to train \acp{FFNN} in a supervised learning approach.

@@

\acp{FFNN} training is seen as a computational search problem. \Acl{HH} as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''. \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.

@@

\begin{itemize}
      \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred to as the \Acl{BHH}.

@@

\begin{itemize}
      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acl{AN}. The focus is on training of \acp{FFNN}. It is shown how training of \acp{FFNN} is seen as an optimisation problem.

>>>>

\Acfp{FFNN} are specific types of \acp{ANN} \cite{ref:reed:1999}. A popular field of focus for studying \acp{ANN} is the process by which these models are trained.  The most common way of training \acp{FFNN} is \index{supervised learning}\textit{supervised learning}, which is a training technique that involves exposing the \acp{ANN} with input and comparing the produced output to that of predefined target data. Training of \acp{ANN} is seen as an optimisation problem. The \ac{ANN} maintains a set of parameters, referred to as ``weights'' and ``biases''. A search algorithm known as a \index{heuristic}\textit{heuristic} \cite{ref:pearl:1984} is used to assign optimal values to the parameters of the \ac{ANN}, such that a specified objective function is minimised. The research presented in this disseration focuses on the development of a specific type of heuristic, called a \acf{HH} to train \acp{FFNN} in a supervised learning approach.

@@

\acp{FFNN} training is seen as a computational search problem. \acf{HH} as defined by Burke et al. \cite{ref:burke:2010} is ``a search method or learning mechanism for selecting or generating heuristics to solve computational search problems''. \acp{HH} is a field of research aimed at the automated selection, combination, adaptation or generation of multiple lower-level heuristics to efficiently solve computational search problems.

@@

\begin{itemize}
      \item A novel heuristic selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acp{FFNN}. The resulting \ac{HH} is referred to as the \acf{BHH}.

@@

\begin{itemize}
      \item \textbf{Chapter~\ref{chap:anns}} provides a literature study on \acp{ANN} and the various components that make up an \acf{AN}. The focus is on training of \acp{FFNN}. It is shown how training of \acp{FFNN} is seen as an optimisation problem.
